---
title: "greedyQ User Experience Survey"
greedyq:
  spec_version: "0.2"
  version: "0.2_2026-09-09_e770a9c"
  organization: "greedyQ Research Team"
theme-settings:
  theme: default
  barposition: top
  barcolor: "#315c8a"
  footer-center: "greedyQ user feedback"
survey-settings:
  show-previous: true
  use-cookies: true
  all-required: false
  start-page: welcome
  highlight-unanswered: true
  capture-metadata: false
  required:
    - consent_choice
    - age
    - used_greedyq
    - use_frequency
    - primary_use
    - ai_host
    - completion_status
    - guide_access
    - overall_satisfaction
    - experience_ratings
    - confidence
    - time_saved
    - had_problem
    - recommend_score
    - use_again
    - withdraw_now
system-messages:
  previous: "Previous"
  next: "Next"
  required: "Please answer the required questions before continuing."
---

--- welcome

# Tell us about your greedyQ experience

This survey is for people who have used greedyQ to create or revise a questionnaire. It takes about four minutes.

```{r}
sd_nav(show_previous = FALSE, label_next = "Read participant information")
```

--- consent

# Participant information and consent

Please read the versioned [participant information and consent](./consent.md). Taking part is voluntary, and you may stop at any time.

```{r}
sd_question(
  id = "consent_choice",
  type = "mc",
  label = "Do you consent to participate in this survey?",
  option = c(
    "Yes, I consent" = "yes",
    "No, I do not consent" = "no"
  )
)
```

```{r}
sd_nav(show_previous = FALSE, label_next = "Continue")
```

--- eligibility

# About your eligibility

```{r}
sd_question(
  id = "age",
  type = "numeric",
  label = "What is your age in years?",
  placeholder = "Age"
)

```

```{r}
sd_question(
  id = "used_greedyq",
  type = "mc",
  label = "Have you used greedyQ to create or revise a questionnaire?",
  option = c(
    "Yes" = "yes",
    "No" = "no"
  )
)
```

--- usage

# How you used greedyQ

```{r}
sd_question(
  id = "use_frequency",
  type = "select",
  label = "How many times have you used greedyQ?",
  option = c(
    "Once" = "once",
    "Two or three times" = "two_three",
    "Four or five times" = "four_five",
    "More than five times" = "more_than_five"
  ),
  label_select = "Choose one"
)

```

```{r}
sd_question(
  id = "primary_use",
  type = "select",
  label = "What was your main reason for using greedyQ most recently?",
  option = c(
    "Create a new survey" = "new_survey",
    "Revise an existing survey" = "revise_survey",
    "Create a survey experiment" = "experiment",
    "Prepare consent or preregistration materials" = "research_documents",
    "Explore or test greedyQ" = "exploration",
    "Something else" = "other"
  ),
  label_select = "Choose one"
)

```

```{r}
sd_question(
  id = "primary_use_other",
  type = "text",
  label = "What was your main reason for using greedyQ?",
  placeholder = "Brief description"
)

```

```{r}
sd_question(
  id = "ai_host",
  type = "select",
  label = "Which AI product did you mainly use with greedyQ?",
  option = c(
    "ChatGPT" = "chatgpt",
    "Claude" = "claude",
    "Codex" = "codex",
    "Claude Code" = "claude_code",
    "Another AI product" = "other",
    "I am not sure" = "not_sure"
  ),
  label_select = "Choose one"
)

```

```{r}
sd_question(
  id = "completion_status",
  type = "mc",
  label = "How far did you get in your most recent use?",
  option = c(
    "I created and tested a complete survey" = "tested_complete",
    "I created a survey draft" = "draft_created",
    "I started but did not get a usable draft" = "no_usable_draft",
    "I was only exploring the workflow" = "exploration_only"
  )
)

```

```{r}
sd_question(
  id = "guide_access",
  type = "mc",
  label = "How did you give the greedyQ instructions to your AI?",
  option = c(
    "I shared the greedyQ repository or START-HERE link" = "repository_link",
    "I attached the self-contained guide file" = "guide_attachment",
    "The instructions were already available in my coding agent" = "local_repository",
    "I am not sure" = "not_sure"
  )
)
```

--- evaluation

# Your experience

```{r}
sd_question(
  id = "overall_satisfaction",
  type = "slider",
  label = "Overall, how satisfied were you with greedyQ?",
  option = c(
    "Very dissatisfied" = 1,
    "Dissatisfied" = 2,
    "Somewhat dissatisfied" = 3,
    "Neither satisfied nor dissatisfied" = 4,
    "Somewhat satisfied" = 5,
    "Satisfied" = 6,
    "Very satisfied" = 7
  )
)

```

```{r}
sd_question(
  id = "experience_ratings",
  type = "matrix",
  label = "How much do you agree with each statement about greedyQ?",
  row = c(
    "It was easy to get started." = "easy_start",
    "The AI asked questions I could understand." = "clear_questions",
    "The preview helped me evaluate the survey." = "useful_preview",
    "The resulting survey matched my decisions." = "decision_fidelity"
  ),
  option = c(
    "Strongly disagree" = 1,
    "Disagree" = 2,
    "Neither agree nor disagree" = 3,
    "Agree" = 4,
    "Strongly agree" = 5
  )
)

```

```{r}
sd_question(
  id = "confidence",
  type = "slider",
  label = "How confident were you that the resulting survey reflected what you wanted?",
  option = c(
    "Not at all confident" = 1,
    "Slightly confident" = 2,
    "Somewhat confident" = 3,
    "Moderately confident" = 4,
    "Very confident" = 5
  )
)

```

```{r}
sd_question(
  id = "time_saved",
  type = "select",
  label = "Compared with your usual way of making a survey, how did greedyQ affect the time required?",
  option = c(
    "It took much more time" = "much_more",
    "It took somewhat more time" = "somewhat_more",
    "It took about the same time" = "same",
    "It saved some time" = "some_saved",
    "It saved a great deal of time" = "great_deal_saved",
    "I cannot compare yet" = "cannot_compare"
  ),
  label_select = "Choose one"
)

```

```{r}
sd_question(
  id = "low_satisfaction_reason",
  type = "textarea",
  label = "What most contributed to your dissatisfaction?",
  placeholder = "Optional detail"
)
```

--- problems

# Problems you encountered

```{r}
sd_question(
  id = "had_problem",
  type = "mc",
  label = "Did you encounter a problem that made it harder to complete your survey?",
  option = c(
    "Yes" = "yes",
    "No" = "no",
    "I am not sure" = "not_sure"
  )
)

```

```{r}
sd_question(
  id = "problem_area",
  type = "select",
  label = "Where did the most important problem occur?",
  option = c(
    "The AI conversation or questions" = "conversation",
    "The survey questions or answer choices" = "questionnaire",
    "The participant preview" = "preview",
    "The generated files" = "generated_files",
    "Deployment or database setup" = "deployment",
    "Something else" = "other"
  ),
  label_select = "Choose one"
)

```

```{r}
sd_question(
  id = "problem_detail",
  type = "textarea",
  label = "What happened, and what would you have expected instead?",
  placeholder = "Please avoid including names, credentials, or private research data"
)
```

--- future_use

# Looking ahead

```{r}
sd_question(
  id = "recommend_score",
  type = "numeric",
  label = "How likely are you to recommend greedyQ to another researcher, from 0 (not at all likely) to 10 (extremely likely)?",
  placeholder = "0 to 10"
)

```

```{r}
sd_question(
  id = "use_again",
  type = "mc",
  label = "Would you use greedyQ for another survey?",
  option = c(
    "Definitely not" = 1,
    "Probably not" = 2,
    "Not sure" = 3,
    "Probably yes" = 4,
    "Definitely yes" = 5
  )
)

```

```{r}
sd_question(
  id = "most_valuable",
  type = "textarea",
  label = "What was the most valuable part of greedyQ for you?",
  placeholder = "Optional"
)

```

```{r}
sd_question(
  id = "improvement",
  type = "textarea",
  label = "What is the single most important improvement we should make?",
  placeholder = "Optional"
)
```

--- participant_control

# Before submitting

You may submit your feedback or withdraw. If you withdraw, you may also ask us to delete the responses associated with this session.

```{r}
sd_question(
  id = "withdraw_now",
  type = "mc",
  label = "What would you like to do?",
  option = c(
    "Submit my feedback" = "submit",
    "Withdraw from the survey" = "withdraw"
  )
)

```

```{r}
sd_question(
  id = "deletion_request",
  type = "mc",
  label = "Should the research team receive a request to delete responses already collected in this session?",
  option = c(
    "Yes, record a deletion request" = "yes",
    "No" = "no"
  )
)
```

--- complete

# Thank you

Your feedback has been submitted. It will be used to improve greedyQ.

--- screened_out

# This survey is not the right fit

This feedback survey is for adults who have already used greedyQ. No product-feedback questions were collected.

--- consent_refused

# Participation declined

No product-feedback responses were collected. You may close this page.

--- withdrawn

# Participation ended

Your session is marked as withdrawn. If you requested deletion, the request has been recorded; this message does not claim deletion is already complete.

--- technical_error

# We could not continue

The survey encountered a technical problem. Please close this page and try again later.
