---
title: "greedyQ Control Gallery"
greedyq:
  spec_version: "0.2"
  version: "0.2_2026-09-10_da78aae"
  organization: "greedyQ"
survey-settings:
  mode: preview
  start-page: controls
---

--- controls

# All surveydown-compatible controls

Use this page to test every control in desktop and mobile preview modes.

```{r}
sd_question(id = "short_text", type = "text", label = "Text", placeholder = "Type here")
```

```{r}
sd_question(id = "long_text", type = "textarea", label = "Textarea", placeholder = "Write more", cols = 50, height = "120px", resize = "vertical")
```

```{r}
sd_question(id = "number", type = "numeric", label = "Numeric", min = 0, max = 100)
```

```{r}
sd_question(id = "single", type = "mc", label = "Single choice", option = c("Alpha" = "a", "Beta" = "b"))
```

```{r}
sd_question(id = "multiple", type = "mc_multiple", label = "Multiple choice", option = c("Alpha" = "a", "Beta" = "b"))
```

```{r}
sd_question(id = "buttons", type = "mc_buttons", label = "Single-choice buttons", option = c("Alpha" = "a", "Beta" = "b"), justified = TRUE)
```

```{r}
sd_question(id = "multi_buttons", type = "mc_multiple_buttons", label = "Multiple-choice buttons", option = c("Alpha" = "a", "Beta" = "b"), direction = "vertical")
```

```{r}
sd_question(id = "image", type = "mc_image", label = "Single image choice", option = c("Blue square" = "blue", "Gold circle" = "gold"), image = c("images/blue.svg", "images/gold.svg"))
```

```{r}
sd_question(id = "multi_image", type = "mc_multiple_image", label = "Multiple image choice", option = c("Blue square" = "blue", "Gold circle" = "gold"), image = c("images/blue.svg", "images/gold.svg"))
```

```{r}
sd_question(id = "menu", type = "select", label = "Select", option = c("Alpha" = "a", "Beta" = "b"), label_select = "Choose one")
```

```{r}
sd_question(id = "labeled_slider", type = "slider", label = "Labeled slider", option = c("Low" = "low", "Middle" = "middle", "High" = "high"), selected = "middle")
```

```{r}
sd_question(id = "numeric_slider", type = "slider_numeric", label = "Numeric slider", option = seq(0, 10, 1), default = 5, pre = "Score: ")
```

```{r}
sd_question(id = "range_slider", type = "slider_numeric", label = "Range slider", option = seq(0, 10, 1), default = c(3, 7), sep = " to ")
```

```{r}
sd_question(id = "one_date", type = "date", label = "Date")
```

```{r}
sd_question(id = "date_range", type = "daterange", label = "Date range")
```

```{r}
sd_question(id = "one_matrix", type = "matrix", label = "Single-choice matrix (seven columns demonstrate mobile chunking)", row = c("First row" = "first", "Second row" = "second"), option = c("Strongly disagree" = 1, "Disagree" = 2, "Somewhat disagree" = 3, "Neutral" = 4, "Somewhat agree" = 5, "Agree" = 6, "Strongly agree" = 7), mobile_columns = 3)
```

```{r}
sd_question(id = "multi_matrix", type = "matrix_multiple", label = "Multiple-choice matrix", row = c("First row" = "first", "Second row" = "second"), option = c("Web" = "web", "App" = "app"))
```

```{r}
sd_question_custom(
  id = "audio_example",
  label = "Audio stimulus (greedyQ extension)",
  output = "gq_audio_example_output",
  value = "gq_audio_example_value"
)
```

```{r}
sd_question_custom(
  id = "video_example",
  label = "Video stimulus (greedyQ extension)",
  output = "gq_video_example_output",
  value = "gq_video_example_value"
)
```

```{r}
sd_question(id = "conditional_choice", type = "mc", label = "Show the conditional text field?", option = c("Yes" = "yes", "No" = "no"))
```

```{r}
sd_question(id = "conditional_text", type = "text", label = "This field appeared immediately", placeholder = "Conditional text")
```

```{r}
sd_nav(page_next = "advanced_controls", previous_mode = "hide", label_next = "Try advanced controls")
```

--- advanced_controls

# greedyQ advanced controls

These deterministic extensions cover common advanced research interactions.

```{r}
sd_question_custom(
  id = "rank_example",
  label = "Rank these priorities",
  output = "gq_rank_example_output",
  value = "gq_rank_example_value"
)
```

```{r}
sd_question_custom(
  id = "sbs_example",
  label = "Rate both versions",
  output = "gq_sbs_example_output",
  value = "gq_sbs_example_value"
)
```

```{r}
sd_question_custom(
  id = "nps_example",
  label = "How likely are you to recommend greedyQ?",
  output = "gq_nps_example_output",
  value = "gq_nps_example_value"
)
```

```{r}
sd_question_custom(
  id = "timing_example",
  label = "Time on this page",
  output = "gq_timing_example_output",
  value = "gq_timing_example_value"
)
```

```{r}
sd_question_custom(
  id = "sum_example",
  label = "Allocate 100 points",
  output = "gq_sum_example_output",
  value = "gq_sum_example_value"
)
```

```{r}
sd_question_custom(
  id = "group_rank_example",
  label = "Group and rank these items",
  output = "gq_group_rank_example_output",
  value = "gq_group_rank_example_value"
)
```

```{r}
sd_question_custom(
  id = "drill_example",
  label = "Choose a location",
  output = "gq_drill_example_output",
  value = "gq_drill_example_value"
)
```

```{r}
sd_question_custom(
  id = "custom_example",
  label = "Custom control based on a built-in template",
  output = "gq_custom_example_output",
  value = "gq_custom_example_value"
)
```

```{r}
sd_nav(page_next = "navigation_controls", label_next = "Try navigation controls")
```

--- navigation_controls

# Navigation controls

This page keeps Previous visible but disabled. Continue becomes available after three seconds.

```{r}
sd_nav(page_next = "complete", previous_mode = "disable", next_mode = "show", next_delay_seconds = 3, label_next = "Continue after the delay")
```

--- complete

# Control test complete

All controls were displayed.
