---
title: "greedyQ Control Gallery"
greedyq:
  spec_version: "0.2"
  version: "0.2_2026-09-10_c4a8405"
  organization: "greedyQ"
survey-settings:
  start-page: controls
---

--- controls

# All surveydown-compatible controls

Use this page to test every control in desktop and mobile preview modes.

```{r}
sd_question(id = "short_text", type = "text", label = "Text", placeholder = "Type here")
```

```{r}
sd_question(id = "long_text", type = "textarea", label = "Textarea", placeholder = "Write more", cols = 50, height = "120px", resize = "vertical")
```

```{r}
sd_question(id = "number", type = "numeric", label = "Numeric", min = 0, max = 100)
```

```{r}
sd_question(id = "single", type = "mc", label = "Single choice", option = c("Alpha" = "a", "Beta" = "b"))
```

```{r}
sd_question(id = "multiple", type = "mc_multiple", label = "Multiple choice", option = c("Alpha" = "a", "Beta" = "b"))
```

```{r}
sd_question(id = "buttons", type = "mc_buttons", label = "Single-choice buttons", option = c("Alpha" = "a", "Beta" = "b"), justified = TRUE)
```

```{r}
sd_question(id = "multi_buttons", type = "mc_multiple_buttons", label = "Multiple-choice buttons", option = c("Alpha" = "a", "Beta" = "b"), direction = "vertical")
```

```{r}
sd_question(id = "image", type = "mc_image", label = "Single image choice", option = c("Blue square" = "blue", "Gold circle" = "gold"), image = c("images/blue.svg", "images/gold.svg"))
```

```{r}
sd_question(id = "multi_image", type = "mc_multiple_image", label = "Multiple image choice", option = c("Blue square" = "blue", "Gold circle" = "gold"), image = c("images/blue.svg", "images/gold.svg"))
```

```{r}
sd_question(id = "menu", type = "select", label = "Select", option = c("Alpha" = "a", "Beta" = "b"), label_select = "Choose one")
```

```{r}
sd_question(id = "labeled_slider", type = "slider", label = "Labeled slider", option = c("Low" = "low", "Middle" = "middle", "High" = "high"), selected = "middle")
```

```{r}
sd_question(id = "numeric_slider", type = "slider_numeric", label = "Numeric slider", option = seq(0, 10, 1), default = 5, pre = "Score: ")
```

```{r}
sd_question(id = "range_slider", type = "slider_numeric", label = "Range slider", option = seq(0, 10, 1), default = c(3, 7), sep = " to ")
```

```{r}
sd_question(id = "one_date", type = "date", label = "Date")
```

```{r}
sd_question(id = "date_range", type = "daterange", label = "Date range")
```

```{r}
sd_question(id = "one_matrix", type = "matrix", label = "Single-choice matrix (seven columns demonstrate mobile chunking)", row = c("First row" = "first", "Second row" = "second"), option = c("Strongly disagree" = 1, "Disagree" = 2, "Somewhat disagree" = 3, "Neutral" = 4, "Somewhat agree" = 5, "Agree" = 6, "Strongly agree" = 7), mobile_columns = 3)
```

```{r}
sd_question(id = "multi_matrix", type = "matrix_multiple", label = "Multiple-choice matrix", row = c("First row" = "first", "Second row" = "second"), option = c("Web" = "web", "App" = "app"))
```

```{r}
sd_question(id = "audio_example", type = "audio", label = "Audio stimulus (greedyQ extension)", src = "https://interactive-examples.mdn.mozilla.net/media/cc0-audio/t-rex-roar.mp3", controls = TRUE, caption = "Example audio with participant controls", transcript = "A short dinosaur roar.")
```

```{r}
sd_question(id = "video_example", type = "video", label = "Video stimulus (greedyQ extension)", src = "https://interactive-examples.mdn.mozilla.net/media/cc0-videos/flower.mp4", controls = TRUE, caption = "Example video with participant controls")
```

```{r}
sd_question(id = "conditional_choice", type = "mc", label = "Show the conditional text field?", option = c("Yes" = "yes", "No" = "no"))
```

```{r}
sd_question(id = "conditional_text", type = "text", label = "This field appeared immediately", placeholder = "Conditional text")
```

```{r}
sd_nav(page_next = "advanced_controls", previous_mode = "hide", label_next = "Try advanced controls")
```

--- advanced_controls

# greedyQ advanced controls

These deterministic extensions cover common advanced research interactions.

```{r}
sd_question(id = "rank_example", type = "rank_order", label = "Rank these priorities", option = c("Ease of use" = "ease", "Speed" = "speed", "Flexibility" = "flexibility"))
```

```{r}
sd_question(id = "sbs_example", type = "side_by_side", label = "Rate both versions", column = c("Current" = "current", "Proposed" = "proposed"), row = c("Clear" = "clear", "Useful" = "useful"), option = c("Low" = 1, "Medium" = 2, "High" = 3))
```

```{r}
sd_question(id = "nps_example", type = "nps", label = "How likely are you to recommend greedyQ?", min = 0, max = 10, low_label = "Not at all likely", high_label = "Extremely likely")
```

```{r}
sd_question(id = "timing_example", type = "timing", label = "Time on this page")
```

```{r}
sd_question(id = "sum_example", type = "constant_sum", label = "Allocate 100 points", option = c("Design" = "design", "Testing" = "testing", "Documentation" = "documentation"), total = 100)
```

```{r}
sd_question(id = "group_rank_example", type = "pick_group_rank", label = "Group and rank these items", option = c("Speed" = "speed", "Trust" = "trust", "Ease" = "ease"), group = c("Essential" = "essential", "Optional" = "optional"))
```

```{r}
sd_question(id = "drill_example", type = "drill_down", label = "Choose a location", option = c("Asia > Korea > Seoul" = "kr_seoul", "Asia > Korea > Busan" = "kr_busan", "Europe > France > Paris" = "fr_paris"), path_separator = " > ")
```

```{r}
sd_question(id = "custom_example", type = "custom", base_type = "mc_buttons", label = "Custom control based on a built-in template", option = c("First" = "first", "Second" = "second"), customization = "Confirmed button-card treatment", custom_class = "gq-custom-button-card")
```

```{r}
sd_nav(page_next = "navigation_controls", label_next = "Try navigation controls")
```

--- navigation_controls

# Navigation controls

This page keeps Previous visible but disabled. Continue becomes available after three seconds.

```{r}
sd_nav(page_next = "complete", previous_mode = "disable", next_mode = "show", next_delay_seconds = 3, label_next = "Continue after the delay")
```

--- complete

# Control test complete

All controls were displayed.
